### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
results - dynamic xrd - added draft paragraph

>>>>

The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed. Thus samples were subjected to dynamic \acrshort{xrd} over their most active rang to observe changes \textit{in-situ}. This allowed the crystallisation to be watched live for seeing how phase evolved over time as the temperature was raised in 5 \degree C increments.
